Clustering analysis and statistics

### 2019-08-16 notebooks/Clustering analysis.Rmd

gheatmap(p,
         pat_dist_bin,
         color = NULL,
         offset = 0.01,
         colnames = FALSE) +
  scale_fill_manual(values = col_palette) + 
  annotate("label", x = 0.27, y = 270, label = "Clade A") +
  annotate("label", x = 0.29, y = 251, label = "Clade B") +
  annotate("label", x = 0.39, y = 167, label = "Clade C") +
  annotate("label", x = 0.38, y = 138, label = "Clade D") +
  annotate("label", x = 0.32, y = 57, label = "Clade E") +
  annotate("label", x = 0.31, y = 31, label = "Clade F")

@@

names(dist_data) <- c("Clade D", "Clade F", "Clade A", "Clade E", "Clade B", "Clade C")

@@

# Import trees
ST10_raw <- read.iqtree("../data/Phylogeny/STs/ST10/iqtree/iqtree.contree")
ST355_raw <- read.iqtree("../data/Phylogeny/STs/ST355/iqtree/iqtree.contree")
ST602_raw <- read.iqtree("../data/Phylogeny/STs/ST602/iqtree/iqtree.contree")
ST744_raw <- read.iqtree("../data/Phylogeny/STs/ST744/iqtree/iqtree.contree")

raw_trees <- list(ST10_raw,
                  ST355_raw,
                  ST602_raw,
                  ST744_raw)

names(raw_trees) <- c("Clade D","Clade E","Clade B","Clade C")

@@

# Generate trees
annotate_tree(
  clean_trees$`Clade B`,
  tree_metadata,
  layout = "rectangular",
  tree_type = "treedata",
  midroot = TRUE,
  line_width = 0.5,
  label_variable = "Location",
  color_variable = "Year",
  shape_variable = "Species",
  bootstrap_var = "Bootstrap",
  clade_label_node = 10,
  clade_label = "18 SNP diff",
  cladelabel_offset = 0.001,
  bootstrap_lab = FALSE,
  tippoint_size = 4,
  label_offset = 0.0002,
  shape_palette = palette_shape,
  color_palette = palette_color,
  node_palette = boot_palette
) +
  xlim(0, 0.009) +
  ggtitle("Clade B, ST602")

>>>>

gheatmap(p,
         pat_dist_bin,
         color = NULL,
         offset = 0.01,
         colnames = FALSE) +
  scale_fill_manual(values = col_palette) + 
  annotate("label", x = 0.26, y = 274, label = "Clade A") +
  annotate("label", x = 0.27, y = 262, label = "Clade B") +
  annotate("label", x = 0.40, y = 167, label = "Clade C") +
  annotate("label", x = 0.39, y = 138, label = "Clade D") +
  annotate("label", x = 0.33, y = 57, label = "Clade E") +
  annotate("label", x = 0.32, y = 31, label = "Clade F")

@@

names(dist_data) <- c("Clade D", "Clade F", "Clade A", "Clade B", "Clade E", "Clade C")

@@

# Import trees
ST10_raw <- read.iqtree("../data/Phylogeny/STs/ST10/iqtree/iqtree.contree")
ST162_A_raw <- read.iqtree("../data/Phylogeny/STs/ST162_A/iqtree/iqtree.contree")
ST355_raw <- read.iqtree("../data/Phylogeny/STs/ST355/iqtree/iqtree.contree")
ST744_raw <- read.iqtree("../data/Phylogeny/STs/ST744/iqtree/iqtree.contree")

raw_trees <- list(ST10_raw,
                  ST162_A_raw,
                  ST355_raw,
                  ST744_raw)

names(raw_trees) <- c("Clade D","Clade A","Clade E","Clade C")

@@

# Generate trees
annotate_tree(
  clean_trees$`Clade A`,
  tree_metadata,
  layout = "rectangular",
  tree_type = "treedata",
  midroot = TRUE,
  line_width = 0.5,
  label_variable = "Location",
  color_variable = "Year",
  shape_variable = "Species",
  bootstrap_var = "Bootstrap",
  clade_label_node = 27,
  clade_label = "18 SNP diff",
  cladelabel_offset = 0.001,
  bootstrap_lab = FALSE,
  tippoint_size = 4,
  label_offset = 0.0002,
  shape_palette = palette_shape,
  color_palette = palette_color,
  node_palette = boot_palette
) +
  xlim(0, 0.009) +
  ggtitle("Clade A, ST162")
